Reviewer comments from PeerJ

### 2015-03-23 PeerJResponse.tex
edits to response

8) Line 150. Why were only 100 bootstrap replicates used for the NJ analysis? 1000 is more typical.\\
\lev{I do not know the answer to this. I don't think that 1000 bootstraps would give us really a difference.}
\mbh{if you still have the input file for this analysis, should be a quick fix and show we're doing everything we can to address reviewer concerns}
\jri{agreed, should be easy to redo. while agree this is silly and i don't think 1000 will change anything, but since it's easy to do it's hard to argue against doing it.}
\lev{I do not have the files as this is something that Tom did with the sequence data that he gathered}
\mbh{o.k., should we ask Tom for this? The only argument we can make for not doing this is that 100 bootstraps are commonly used, but this makes us sound pretty unaccommodating}

>>>>

8) Line 150. Why were only 100 bootstrap replicates used for the NJ analysis? 1000 is more typical.\\

\res{We have conducted our NJ analysis with 1000 rather than 100 bootstraps and results are qualitatively very similar.}
